Results

### 2024-03-04 Model/hybrid.qmd
adding hybrid fits from past few days

folder_names <- c("e1_hybrid_n_iter_250_ntry_200_0637",
"e1_hybrid_n_iter_60_ntry_150_2335",
"e1_hybrid_n_iter_200_ntry_300_0741",
"e1_hybrid_n_iter_150_ntry_150_4749","e1_hybrid_n_iter_100_ntry_100_1435")

@@

folder_names <- c("e2_hybrid_n_iter_60_ntry_150_3658","e2_hybrid_n_iter_250_ntry_200_0540","e2_hybrid_n_iter_150_ntry_150_2904","e2_hybrid_n_iter_100_ntry_100_3211")

@@

folder_names <- c("e3_hybrid_n_iter_150_ntry_150_1757","e3_hybrid_n_iter_250_ntry_200_4300","e3_hybrid_n_iter_60_ntry_150_0946","e3_hybrid_n_iter_100_ntry_100_0545")

>>>>

# folder_names <- c("e1_hybrid_n_iter_250_ntry_200_0637",
# "e1_hybrid_n_iter_60_ntry_150_2335",
# "e1_hybrid_n_iter_200_ntry_300_0741",
# "e1_hybrid_n_iter_150_ntry_150_4749","e1_hybrid_n_iter_100_ntry_100_1435","e1_hybrid_n_iter_400_ntry_300_3744")

folder_names <- list.files(here("data/abc_reject"),pattern="e1_hyb*")

@@

# folder_names <- c("e2_hybrid_n_iter_60_ntry_150_3658","e2_hybrid_n_iter_250_ntry_200_0540","e2_hybrid_n_iter_150_ntry_150_2904","e2_hybrid_n_iter_100_ntry_100_3211")

folder_names <- list.files(here("data/abc_reject"),pattern="e2_hyb*")

@@

# folder_names <- c("e3_hybrid_n_iter_150_ntry_150_1757","e3_hybrid_n_iter_250_ntry_200_4300","e3_hybrid_n_iter_60_ntry_150_0946","e3_hybrid_n_iter_100_ntry_100_0545")

folder_names <- list.files(here("data/abc_reject"),pattern="e3_hyb*")

### 2024-03-04 Sections/Intro.qmd
adding hybrid fits from past few days

In project 1, I applied model-based techniques to quantify and control for the similarity between training and testing experience, which in turn enabled us to account for the difference between varied and constant training via an extended version of a similarity based generalization model. In project 2, we will go a step further, implementing a full process model capable of both 1) producing novel responses and 2) modeling behavior in both the learning and testing stages of the experiment. Project 2 also places a greater emphasis on extrapolation performance following training. Although varied training has often been purported to be particularly beneficial for generalization or transfer, few experiments have compared varied and constant training in contexts with unambiguous extrapolation testing.

>>>>

A longstanding issue across both science and instruction has been to understand how various aspects of an educational curriculum or training program influence learning acquisition and generalization. One such aspect, which has received a great deal of research attention,  is the variability of examples experienced during training.

Although varied training has often been purported to be particularly beneficial for generalization or transfer, few experiments have compared varied and constant training in contexts with unambiguous extrapolation testing.
